---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = "man/figures/README-"
)
```

## Overview

shopr is a collection of functions that make it easy to interact with the [Shopify REST Admin API](https://help.shopify.com/en/api/reference) from R. Currently, shopr only supports *read* operations (i.e. HTTP GET requests).

## Installation

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ben519/shopr")
```

## Setup
To use the Shopify API, you first need to 

1. [Create a Shopify Partner Account](https://help.shopify.com/en/api/getting-started/making-your-first-request#create-a-shopify-partner-account)
2. [Create a Development Store](https://help.shopify.com/en/api/getting-started/making-your-first-request#create-a-development-store) (Recommended but not necessary)
3. [Generate API credentials from the Shopify admin](https://help.shopify.com/en/api/getting-started/making-your-first-request#generate-api-credentials-from-the-shopify-admin)

It'd be wise to read Shopify's [Getting Started](https://help.shopify.com/en/api/getting-started) article before tinkering with this package.

## Usage

### API Credentials
The functions in this package require three parameters to connect to a shop:

1. shopURL (e.g. "https://my-test-store.myshopify.com")
2. APIKey (e.g. "a1b2c3")
3. APIPassword (e.g. "d4e5g6")

For many functions, these are the *only* required parameters, although many additional parameters may be given.

### Example Use
Perhaps the most useful function in this package is `shopr_get_orders()`. Here's the simplest way to use it.

```{r eval = FALSE}
library(shopr)

shopr_get_orders(
  shopURL = "https://my-test-store.myshopify.com", 
  APIKey = "abc123", 
  APIPassword = "def456"
)
```

This returns a list of 

- *orders* (a data.table of orders)
- *discount_applications* (a data.table of discount applications associated with orders)
- *discount_codes* (a data.tabe of discount codes associated with orders)
- *note_attributes* (a data.table of note attributes associated with orders)
- *tax_lines* (a data.table of tax lines associated with orders)
- *line_items* (a data.table of line items associated with orders)
- *shipping_lines* (a data.table of shipping lines associated with orders)
- *fulfillments* (a data.table of fulfillment details associated with orders)
- *refunds* (a data.table of refunds associated with orders)

For shops with many orders, this is *a lot* of data. You can filter the fields or rows using filter criteria like *created_at_min*, *processed_at_min*, *fulfillment_status*, and other parameters. See `?shopr_get_orders` for more details.


### Pagination
Some resources (e.g. orders, products, etc.) require pagination to return a large result set. As an example, suppose we have a shop with 1001 products and we want to GET every product. Shopify allows a max return size of 250 items per query (`limit_per_page = 250`), so we'll need to make 5 queries to retrieve all the products. shopr handles pagination internally so you don't have to. There are two ways shopr does this.

#### 1. Using *since_id*
Some methods like `shopr_get_orders()` and `shopr_get_products()` provide a parameter, *since_id*, which is 0 by default. If you request to get all the orders for a shop, shopr will make successive calls to Shopify's API fetching orders in chunks of 250, updating *since_id* to keep track of what orders have already been returned. (Note that Shopify orders results by id when *since_id* is used.) [This is Shopify's preferred method for pagination](https://developers.shopify.com/changelog/paginated-requests-may-now-be-subject-to-additional-api-throttling). shopr uses *count* methods like `shopr_get_orders_count()` and `shopr_get_products_count()` to know in advance how many pages of records to request. shopr stiches the chunks of results together before returning them.

#### 2. Using *page*
Some methods like `shopr_get_inventory_levels()` uses *page* instead of *since_id*. (*since_id* is not yet implemented for this resource.) *page* is 1 by default and increments by 1 until no more results are returned or the parameter *max_pages* is reached.

See [this article for details about API rate limits](https://help.shopify.com/en/api/reference/rest-admin-api-rate-limits).
